SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-14 docs/questioning.tex
page numbers
new figure to and description to address the CSRF issue

\maketitle
\begin{abstract}

@@

Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from now on. In an {\sc sql} injection
attack the injected code becomes part of a query that
finally reaches the database where it is executed.
In the case of a {\sc csrf} attack the functionality dictated by
the malicious response is performed.

@@

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps-new.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
\end{figure*}

>>>>

\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\begin{abstract}

@@

Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from now on. In an {\sc sql} injection
attack the injected code becomes part of a query that
finally reaches the database where it is executed.

@@

In the case of a {\sc csrf} attack, consider a
user who visits a page, where attackers have managed
to inject {\sc html} code that contains a hidden
request in the way we described in Section~\ref{sec:attacks}.
If an authenticated user visits this web page, then the
malicious request will reach the application ({\sc csrf} 2) and
the functionality dictated by the malicious response will
be performed.

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps-newer.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
{\sc ub} (at the browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
{\sc dbal} (at the database abstraction layer):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
\end{figure*}
